Microtransaction is the Future of MMORPGs

### 2022-04-27 outputs/paper/paper.Rmd
Added a datasheet for the dataset in paper.Rmd. Added 00-simulation.R. Added a PDF copy of the survey used to collect the dataset at inputs/survey/bdo_survey.pdf.

---
title: "(TEMP) Online Video Game Monetization Schemes and Its Relationship to the Consumers"
author: 
  - Tian Yi Zhang
thanks: "Code and data are available at: https://github.com/zhan7818/bdo_monetization"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Advertisement and monetization schemes are essential to obtaining a stable revenue stream and ensuring the continued surival of an online video game. We obtain data through a survey distributed in several online communities for the massively multiplayer online game known as Black Desert Online and analyze it throuhg several graphs, tables, and a model in this paper. (TODO) Sentence about findings. (TODO) Sentence about implications. (TODO) Keywords:"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

Just a decade or two ago, singleplayer-driven content was the predominant
focus in the video game industry. This was mostly a product of the time, as the
infrastructures needed to support online-based video games were yet to be
fully developed. More importantly, what this also meant was a lack of 
post-launch updates being delivered for a game, as developers also lacked means
to deliver constant updates effectively into the hands of the consumers. As a
result, most video games received little to no post-launch updates aside from
one or two major expansions to their games that contained sufficient content
to be put on the shelves as add-ons to the original purchase.
Despite this, consumers back then were generally content with the amount of 
content they received for their purchases.

As the years went by and networking structures matured, however, more and more
video game developers started focusing more on the online aspects of gaming.
The number of multiplayer-focused video games in the market started to steadily
increase. Now, in an era of live service online video games, developers are 
pressured to continuously produce and deliver new and exciting content on a 
consistent schedule in order to compete with other products. This need to
create more content for a game means that development resources are constantly
required, and online focused games can no longer afford to charge their
consumers a simple upfront fee; live service video games must find an effective
and profitable monetization scheme in order to fund their continued development.

@@

All tables and graphs presented in this paper are produced using the 
statistical programming language `R` [@citeR]. The `knitr` [@citeknitr] and
`kableExtra` [@citeKableE] packages are used for tables, and the `ggplot`
[@citeggplot2] package is used for graphs.

TODO: add in some references that support claims about general transition from 
singleplayer to multiplayer in video game industry.

@@

Due to the lack of APIs provided by Pearl Abyss that concerns the subject of
this paper, convenience sampling is used to collect data from the general
playerbase for the game. The survey is created in Google Forms and is
distributed to Black Desert Online players on Steam discussion, Black Desert
Online forum board, and the Black Desert Online subreddit on Reddit. The survey
consists of questions mostly regarding the respondents' amount of spending in
the various monetization models employed by Black Desert Online, as well as
some general background information regarding each respondent and their in-game
characters. The survey questions could be largely divided into the following set
of topics:

@@

Due to having a variety of ways for consumers to spend real world currencies in
BDO, a considerable variation of money spent on the game is expected for
respondents of the survey.
This is demonstrated in Figure \@ref(tab:graph1), where we can see that the
majority of respondents spend less than $1000 USD in the pearl shop, but there
are also quite a few respondents that fall outside of that range by a
substantial amount. 
Note that it is unwise to simply categorize these responses as simple outliers
and exclude them from the dataset, as we must consider the phenomenon of
"whales". This idea is also further explored in Section \@ref(discussion).

@@

## Free Game Package

@@

This is further elaborated upon in Table \@ref(tab:table3), which summarises
the dataset based on whether the respondent's spending status is considered
`completely free` if they obtained the free package for the game and did not
spent money on other game packages nor in the pearl shop, and `partially free`
if they obtained the free package for the game but spent money on other
game packges and/or in the pearl shop.
We can see from Table \@ref(tab:table3) that despite having a lower average
spending in both the pearl shop and game packages, the "partially free" players
still spent a substantial amount of money on further purchases for the game:
On average, for "partially free" respondents,
the amount of money spent on game package purchases accounts for only 6% of
their total spending on BDO. We observe a similar statistic for players who
did not obtain a free package for the game, whose spending on game packages
accounts for only 5% of their total spending on BDO.

@@

As discussed in Section \@ref(free-game-package), roughly 66% of players who obtained
the free package for the game ended up spending real world currencies in the
pearl shop. This shows that the majority of players will spend money on a game
even when it is free-to-play, providing further incentives for MMORPG publishers
to abandon charging upfront fees.

@@

According to Connick [@citebalance], `whale` is originally a term in sales
used to refer to clients that bring in substantially more business than
an average client does.
The video game industry has borrowed this termto refer to players
who spend an exorbitant amount of real world currency in a game.
As alluded to in the beginning paragraphs of Section
\@ref(preliminary-analysis), we
observer several outliers in the dataset with drastically more in-game spending
than the rest of the respondents. These outliers are most likely the
aforementioned whales.

@@

Whales are very rare compared to the average player. Unfortunately,
due to the limited
number of responses generated by the survey, 
an analysis on whales in particular was
not able to be conducted in this paper. Possible extensions of this paper could
focus on gathering a large enough dataset in the hopes that it contains a
sufficient sample of whale respondents to fit a model to.

@@

>>>>

---
title: "Microtransaction is the Future of MMORPGs"
author: 
  - Tian Yi Zhang
thanks: "Code and data are available at: https://github.com/zhan7818/bdo_monetization"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Advertisement and monetization schemes are essential to obtaining a stable revenue stream and ensuring the continued surival of an online video game. We obtain data through a survey distributed in several online communities for the massively multiplayer online game known as Black Desert Online and analyze it throuhg several graphs, tables, and a model in this paper. Results show a positive correlation between players' total playtimes, rated importance of subscription items, and their total monetary spending in the in-game cash shop. Players with a female main character in the game spend on average 9.23% more real world currency on cosmetic items in-game. On average, upfront cost for the game accounts for only 5-6% of a player's total spending on the game. These findings suggest that MMORPGs should release with an upfront cost before transitioning to free-to-play later down the line. The introduction of more than one type of subscription items becomes marginally less profitable. Further analysis on the topic of whales is recommended. Keywords: VP, BK, OM, Whale, MMORPG, Subscription, Pearl Shop, Central Market, Black Desert Online, Gender, Microtransaction"
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

Up until a decade or two ago, singleplayer-driven content was the predominant
focus in the video game industry. This was mostly a product of the time, as the
infrastructures needed to support online-based video games were yet to be
fully developed. More importantly, what this also meant was a lack of 
post-launch updates being delivered for a game, as developers also lacked means
to deliver constant updates effectively into the hands of the consumers. As a
result, most video games received little to no post-launch updates aside from
one or two major expansions to their games that contained sufficient content
to be put on the shelves as add-ons to the original purchase.
Despite this, consumers back then were generally content with the amount of 
content they received for their purchases.

The drastic shift towards online gaming started in the early 2000s, according
to Chikhani [@citechik]. During that time period, networking structures matured
 and internet services became more affordable. As such, more and more
video game developers started focusing more on the online aspects of gaming.
The number of multiplayer-focused video games in the market started to steadily
increase. Now, in an era of live service online video games, developers are 
pressured to continuously produce and deliver new and exciting content on a 
consistent schedule in order to compete with other products. This need to
create more content for a game means that development resources are constantly
required, and online focused games can no longer afford to charge their
consumers a simple upfront fee; live service video games must find an effective
and profitable monetization scheme in order to fund their continued development.

@@

All tables and graphs presented in this paper are produced using the 
statistical programming language `R` [@citeR]. The `knitr` [@citeknitr] and
`kableExtra` [@citeKableE] packages are used for the tables, and the `ggplot`
[@citeggplot2] and `cowplot` [@citecow] packages are used for the graphs.

@@

Due to the lack of APIs provided by Pearl Abyss that concerns the subject of
this paper, convenience sampling is used to collect data from the general
playerbase for the game. The survey is created in Google Forms and is
distributed to Black Desert Online players on Steam discussion, Black Desert
Online forum board, and the Black Desert Online subreddit on Reddit.^[A PDF
copy of the survey can be found in the github repo for this paper in 
inputs/survey/bdo_survey.pdf.]
The survey
consists of questions mostly regarding the respondents' amount of spending in
the various monetization models employed by Black Desert Online, as well as
some general background information regarding each respondent and their in-game
characters. The survey questions could be largely divided into the following set
of topics:

@@

Due to having a variety of ways for consumers to spend real world currencies in
BDO, a considerable variation of money spent on the game is expected for
respondents of the survey.
This is demonstrated in Figure \@ref(fig:graph1), where we can see that the
majority of respondents spend less than $1000 USD in the pearl shop, but there
are also quite a few respondents that fall outside of that range by a
substantial amount. 
Note that it is unwise to simply categorize these responses as simple outliers
and exclude them from the dataset, as we must consider the phenomenon of
"whales". This idea is also further explored in Section \@ref(discussion).

@@

## Free Game Package vs Microtransaction

@@

This is further elaborated upon in Table \@ref(tab:table3), which summarises
the dataset based on whether the respondent's spending status is considered
`completely free` if they obtained the free package for the game and did not
spent money on other game packages nor in the pearl shop, and `partially free`
if they obtained the free package for the game but spent money on other
game packges and/or in the pearl shop.
We can see from Table \@ref(tab:table3) that despite having a lower average
spending in both the pearl shop and game packages, the "partially free" players
still spent a substantial amount of money on further purchases for the game:
On average, for "partially free" respondents,
the amount of money spent on game package purchases accounts for only 6% of
their total spending on BDO. We observe a similar statistic for players who
did not obtain a free package for the game, whose spending on game packages
accounts for only 5% of their total spending on BDO.
In contrast, microtransactions in BDO accounts for roughly 95% of the total
revenue, as show in table \@ref(tab:table4), a staggeringly high difference.

@@

As discussed in Section \@ref(free-game-package-vs-microtransaction),
roughly 66% of players who obtained
the free package for the game ended up spending real world currencies in the
pearl shop. This shows that the majority of players will spend money on a game
even when it is free-to-play, providing further incentives for MMORPG publishers
to abandon charging upfront fees.

@@

According to Connick [@citebalance], `whale` is originally a term in sales
used to refer to clients that bring in substantially more business than
an average client does.
The video game industry has borrowed this termto refer to players
who spend an exorbitant amount of real world currency in a game.

As alluded to in the beginning paragraphs of Section
\@ref(preliminary-analysis), we
observer several outliers in the dataset with drastically more in-game spending
than the rest of the respondents. These outliers are most likely the
aforementioned whales.

@@

Whales are rare but their impact have not gone unnoticed. In fact, catering to 
whales is not a new
strategy for publishers by any means, as demonstrated by Jernström [@citepocket] 
, who is well versed in this type of monetisation and
has created a thorough guide for other publishers to follow suit. It is apparent
that publishers are already catching on to these whales and the best strategy
to appeal to them. This should state the significance of whales as the highest
potential source of income for a video game.

Unfortunately, due to the limited
number of responses generated by the survey, 
an analysis on whales in particular was
not able to be conducted in this paper. Possible extensions of this paper could
focus on gathering a large enough dataset in the hopes that it contains a
sufficient sample of whale respondents to fit a model to.

@@

# Datasheet for the Dataset

Extract of the questions from @gebru2021datasheets

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - This dataset was created to be used to analyze the various ways of monetisations that the video game Black Desert Online employs. Due to the lack of APIs and useful tracking tools provided by Pearl Abyss--the developers behind Black Desert Online--A survey was used instead to obtain this dataset through convenience sampling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The survey used to collect the dataset was created by Tian Yi Zhang, a undergraduate student at the University of Toronto and the author of this paper.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - No organization funded the creation of the dataset.
4. *Any other comments?*
    - None.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each instance in the dataset represent a player of the video game Black Desert Online.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 178 male respondents, 25 female respondents, and 5 respondents of other genders.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of instances. It is obtained through convenience sampling from the larger set of Black Desert Online players on the North American and European servers. Since the dataset is obtained through convenience sampling, it is not representative of the total population in terms fof geographical coverage or any stratification. The choice of convenience sampling is due to the lack of APIs and useful tracking tools provided by Pearl Abyss, the developers behind Black Desert Online.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	-  Each instance of data consists of a player's age, gender, total playtime in the game and on their main character, their rated importance of various subscription items in the game, and their total spending on various types of items in the game.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- the gender is either male, female, or other.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- There is lack of female and other genders in certain age groups in the dataset due to insufficient sample size.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- There are no relationships between individual instances.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- None.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- The sample size is unequal for female and male respondents. This unequal sample size does negatively affect the assumption of equal variances. Furthermore, lack of detailed statistic tracking tools and APIs provided by Pearl Abyss--the developer of Black Desert Online--means that playtime and most monetary questions in the survey rely on the respondents' best estimates. 
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- Breakdown of the monetary transcations of each player might be considered a confidential data by Pearl Abyss. However, the survey was designed to be as transparent with the respondents as possible, and no data that could be linked back to the respondents were included in the survey nor in the final paper.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- The dataset does not contain any offensive or insulting data.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- The datasets are split by age groups and gender as self-identified by the respondents.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- It is entirely impossible to identify individuals from the dataset.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- The datasets do not contain data that might be considered sensitive in any way.
16. *Any other comments?*
	- None.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online. The data was reported by the respondents based on their best estimates.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online. The data was reported by the respondents based on their best estimates. Google Forms is used to produce the survey.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Convenience sampling was used due to lack of detailed statistic tracking tools and APIs provided by Pearl Abyss.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- No one but the author is involved in the data collection process.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected over the span of four days from April 18, 2022 to April 21, 2022.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No ethical review processes were conducted. Subreddit moderators were consulted for permission of posting the survey.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Respondents were informed of the purpose of the data collection: "I wish to study the different monetization methods that BDO employs. Due to the lack of proper APIs provided by Pearl Abyss, I have resorted to surveys instead."
	- "To be clear, there will not be any information present in the final paper that can be used to link the data back to the original respondents."
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Since data collection is through a survey, consent was explicitly provided when respondents clicked the survey link.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Respondents can revoke consent by simply exiting the survey.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A.
12. *Any other comments?*
	- None.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Certain variables names were shortened in Google Spreadsheet before the dataset is used for analysis in this paper.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is accessable in the github link provided in this paper.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- statistical programming language R [@citeR] was used to preprocess the datasets.
	- Google Spreadsheet is publicly available for use by registering a Google account.
4. *Any other comments?*
	- None.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- At the time of writing this, only this paper has utilized the dataset.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The repository for this paper, which uses the datasets, are available at https://github.com/zhan7818/bdo_monetization.
3. *What (other) tasks could the dataset be used for?*
	- The datasets could be used to modeling or finding relationship between total in-game spending and age groups.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- None.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The datasets should not be used in an effort to harass or discriminate against the general Black Desert Online community nor should it be used to misrepresent information about the said community.
6. *Any other comments?*
	- None.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Since there dataset is publicly available through the github link, yes.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed on Tian Yi Zhang's github page, along with this paper: https://github.com/zhan7818/bdo_monetization.
3. *When will the dataset be distributed?*
  - The datasets used in this paper is distributed in 2022.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a MIT license.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No restrictions are placed on the dataset.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- None.
7. *Any other comments?*
	- None.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Tian Yi Zhang is hosting the dataset on the github link at https://github.com/zhan7818/bdo_monetization.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The creator of the datasets, Tian Yi Zhang, can be contacted at tianyi.zhang6546@gmail.com.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- As of writing this datasheet, no explicit erratum have been spotted.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Any updates will be posted on the github page used to host this paper which include the datasets.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the datasets (if there will be any) will be kept as a record on github.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- One should contact Tian Yi Zhang, the author of the dataset.
8. *Any other comments?*
	- None.

# Additional Details

Code and data available at: https://github.com/zhan7818/bdo_monetization

- PDF copy of the survey used in this paper is available in
inputs/survey/bdo_survey.pdf

- A simulation of the dataset was conducted in scripts/00-simulation.R which
helped formulate plans for analysis involving the actual dataset.

- Dataset was cleaned in scripts/01-data_cleaning.R
